Name

### 2020-04-01 research-cv/research-cv.tex
2 page

%.bst file
\bibliographystyle{ieeetr} %custom bst file

@@

\noindent\textbf{University}\\
\textbf{Master of Science $\sq$ Major} \hfill{\textit{Date}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Thesis: }
    \item[]Advisor: %committee
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University}\\
\textbf{Bachelor of Science $\sq$ Major and distinction(s)} \hfill{\textit{}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Capstone: }
    \item[] Advisor: Leo M. Bobek
\end{itemize}

%academic positions 
\section*{Research Experience}
\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor} \hfill{\textit{July 2015 - }}\\
Advanced fuel cycle analysis; risk assessment; neutronics; nonproliferation; scientific computing
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\indent\indent Coordinator - NPP Decommissioning and Used Fuel Management Certificate \hfill{\textit{August 2019 - }}
    \item[]\indent\indent Affiliate - Boise State University Energy Policy Institute \hfill{\textit{August 2019 - }}
    \item[]\indent\indent State of Idaho Professional Engineer, Faculty Restricted \hfill{\textit{October 2019 - }}
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Postdoctorate Researcher} \hfill{\textit{February 2009 - July 2012}}\\
A safeguards methodology was developed for remotely-handled nuclear materials facilities that proposes functional design components and a risk-informed framework in an effort to integrate safeguards with safety and security into facility design.
\vspace*{.75\baselineskip}

\noindent\textbf{The University of Tokyo $\sq$ Department of Nuclear Engineering/Management}\\
\textbf{Research Associate} \hfill{\textit{August 2007 - January 2009}}\\
Mathematical models for mass transport in the engineered barrier system of a high-level nuclear waste repository are established for bentonite extrusion and radionuclide transport under different environmental conditions to assess potential impacts on performance assessment.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Postdoctorate Researcher} \hfill{\textit{February 2007 - April 2007}}\\
Mathematical modeling of mass transport in the engineered barrier system of a high-level nuclear waste repository continued, to assess the potential of extruding bentonite to confine radionuclides.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Doctoral Candidate} \hfill{\textit{August 2005 - December 2006}}\\
The dissertation thesis focused on the mathematical modeling of mass transport in the engineered barrier system of a high-level nuclear waste repository. A mass transport model was established for radionuclides in a porous medium, bentonite extrusion model in a planar fracture to assess the potential to confine radionuclides.

\section*{Related Research Experience}
\noindent\textbf{Earth Sciences Division $\sq$ Lawrence Berkeley National Laboratory}\\
\textbf{Intern} \hfill{\textit{July 2001 - February 2002}}\\
Conducted data analysis for chaotic modeling of water flow in the unsaturated zone.
\vspace*{.75\baselineskip}

\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
\textbf{Major Qualifying Project} \hfill{\textit{August 1995 - May 1996}}\\
The Major Qualifying Project synthesizes previous undergraduate studies to solve problems or perform tasks in the major field and communicate results effectively. For this project, a logic algorithm was developed for reactivity derived from point kinetics equations and a programmable logic controller was modified for real time collection of data during nuclear reactor operation for use with experimental coursework and maintenance procedures.

\section*{Related Professional Experience}
\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
\textbf{Assistant Radiation Safety Officer} \hfill{\textit{October 1996 - August 1999}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Responded to emergencies concerning incidents involving radioactive material
    \item[]Maintained records of radiation exposures and dosimetry to campus personnel
    \item[]Maintained the full and current inventory of radioisotopes
    \item[]Performed calibrations for radiation detectors
    \item[]Instructed all radiological and nuclear reactor laboratory safety training
    \item[]Performed secretarial duties for Radiation, Health, and Safety Committee
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
\textbf{Senior Nuclear Reactor Operator \#70145} \hfill{\textit{August 1994 - August 1999}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Operated the university nuclear reactor for experimental research projects
    \item[]Trained reactor operator license candidates
    \item[]Performed corrective and preventative maintenance of reactor systems
    \item[]Modified operator training program to a computer based system
\end{itemize}

\section*{Awarded Projects} %chronologically
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item Lee Ostrom (PI), Richard N. Christensen, R. A. Borrelli, Haiyan Zhao (co-PIs) - University of Idaho. ORED Fall 2019 EIS: Portable XFR for use in supporting material research. ORED Equipment and Infrastructure Support. \textbf{\$40,000.} 2019.12.01 - 2020.11.30
    \item R. A. Borrelli (PI) - University of Idaho, Mark. D. DeHart (co-PI) - Idaho National Laboratory. Application and enhancement of MAMMOTH depletion capabilities. \textbf{\$36,894.} 2020.01.13 - 2020.12.31
    \item Richard N. Christensen (PI), R. A. Borrelli, Michael G. McKellar, Michael Haney, David Arcilesi (co-PIs) - University of Idaho, Richard Jacobson (co-PI) Idaho State University. NuScale Simulator at the Center for Advanced Energy Studies. Department of Energy Scientific Infrastructure Support for Consolidated Innovative Nuclear Research. \textbf{\$285,763.} 2019.10.01 - 2020.09.30
    \item R. A. Borrelli (PI) - University of Idaho, Dennis D. Keiser, Jr., (co-PI) - Idaho National Laboratory. Graduate Research Assistantship: Connecting U-Mo Fuel Processing, Microstructure, and Irradiation Performance. \textbf{\$52,070.57.} 2018.10.01-2019.09.30
    \item R. A. Borrelli (PI), Richard N. Christensen (co-PI) - University of Idaho, Brian T. Jaques (co-PI) - Boise State University, Piyush Sabharwall (co-PI) - Idaho National Laboratory, Mark Delligatti (co-PI) - Table Rock, LLC, Sakae Casting USA, LLC (co-PI). Modeling and design of borated aluminium cask for used fuel cooling. Idaho Global Entrepreneurial Mission (IGEM) - Idaho Commerce, \textbf{\$237,898.} 2018.01.01-2019.05.31
    \item R. A. Borrelli (PI) - University of Idaho, Dennis D. Keiser, Jr., (co-PI) - Idaho National Laboratory. Graduate Research Assistantship: Connecting U-Mo Fuel Processing, Microstructure, and Irradiation Performance. \textbf{\$36,180.} 2017.11.01-2018.05.31
    \item R. A. Borrelli (PI), Lee Ostrom (Senior Advisor) - University of Idaho, Stephen G. Johnson (Senior Advisor) - Idaho National Laboratory. Performance assessment of americium as fuel in radioisotope thermoelectric generators for deep space exploration. Idaho NASA EPSCoR Research Initiation Grant. \textbf{\$55,000.} 2017.08.01-2018.04.30
    \item Kelley Verner (PI), R. A. Borrelli, Marc T. Skinner, Emma Redfoot, Jieun Lee, Seth Dustin, John Peterson (co-PIs) - University of Idaho. Increasing the Go-on Rate in Southeast Idaho Through the Nexus of Food, Energy, and Water. University of Idaho Vandals Big Ideas Project. \textbf{\$23,984.} 2017.07.01-2018.06.30
    \item R. A. Borrelli (PI) - University of Idaho, Jason Hales (co-PI) - Idaho National Laboratory. Graduate Research Assistantship: Idaho National Laboratory Code Documentation. \textbf{\$35,435.} 2016.10.01-2017.06.30
    \item Vivek Utgikar (PI), Fatih Aydogan, Krishnan Raja, Raghunath Kanakala, R. A. Borrelli, Haiyan Zhao, Matthew Swenson (co-PIs) - University of Idaho. University of Idaho Nuclear Engineering Faculty Development Program. United States Regulatory Commission Faculty Development Grant. \textbf{\$434,048.} 2015.09.29 - 2019.09.30
\end{enumerate}

\section*{Equipment Acquisitions}
\noindent University of Idaho, Idaho State University, Idaho National Laboratory. Western Services Corporation Pressurized Water Nuclear Reactor Simulator.

\section*{Thesis Committees}
\subsection*{Major Professor}
\noindent\textit{Current}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Kelley Verner, Ph.D. Candidate - Materials science and nuclear fuels analysis
    \item[]Joseph Christensen, Ph.D. - Criticality safety modeling
    \item[]John Peterson, Ph.D - Nuclear cybersecurity
    \item[]J. Seth Dustin, MS - Satellite RTG performance assessment
    \item[]Olin Calvin, Ph.D. - Enhancement of MAMMOTH depletion capabilities
    \item[]Teyen Widdicombe, Ph.D. - RTG satellite design
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]John Peterson, MS - Molten salt reactor neutronics design
    \item[]Emma Redfoot, MS - Allocating heat and electricity in a nuclear renewable hybrid energy system coupled with a water purification system
    \item[]Jieun Lee, MS - Risk-informed safeguards of pyroprocessing for advanced nuclear fuel concepts
    \item[]Trevor MacLean, MEng - Cybersecurity modeling of non-critical nuclear power plant instrumentation
    \item[]Malachi Tolman, MEng - INL BISON code documentation
\end{itemize}

\subsection*{Member}
\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]D. Devin Imholte, MS - Conceptual design of the Advanced Test Reactor non-destructive examination system
    \item[]John Biersdorf, MEng - Precipitation changes to Idaho National Laboratory over time
    \item[]Winfred Sowah, MS - Thermal behavior of cold plated storage cask for light water reactor nuclear fuels
    \vspace*{.05in}
    \item[]\textit{Idaho State University}
    \item[]Pedro Mena, MS - Reactor transient classification using machine learning 
\end{itemize}

\section*{Refereed Journal Publications}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{pr1}.
    \item\bibentry{bor20b}.
    \item\bibentry{bor20c}.
    \item\bibentry{bor19a}.
    \item\bibentry{bor19b}.
    \item\bibentry{bor19c}.
    \item\bibentry{bor18a}.
    \item\bibentry{bor17a}.
    \item\bibentry{bor17b}.
    \item\bibentry{bor16a}.
    \item\bibentry{bor14a}.
    \item\bibentry{bor14b}.
    \item\bibentry{bor14c}.
    \item\bibentry{bor13a}.
    \item\bibentry{bor13b}.
    \item\bibentry{bor11a}.
    \item\bibentry{bor08a}.
    \item\bibentry{bor08b}.
\end{enumerate}

\section*{Book Contribution}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{bkbor19}.
    \item\bibentry{bkbor15}.
\end{enumerate}

\section*{Refereed Conference Proceedings}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cfbor19a}.
    \item\bibentry{cfbor19b}.
    \item\bibentry{cfbor19c}.
    \item\bibentry{cfbor19d}.
    \item\bibentry{cfbor19e}.
    \item\bibentry{cfbor18a}.
    \item\bibentry{cfbor18b}.
    \item\bibentry{cfbor18c}.
    \item\bibentry{cfbor18d}.
    \item\bibentry{cfbor17a}.
    \item\bibentry{cfbor17b}.
    \item\bibentry{cfbor17c}.
    \item\bibentry{cfbor17d}.
    \item\bibentry{cfbor17e}.
    \item\bibentry{cfbor16a}.
    \item\bibentry{cfbor13a}.
    \item\bibentry{cfbor13b}.
    \item\bibentry{cfbor12a}.
    \item\bibentry{cfbor11a}.
    \item\bibentry{cfbor10a}.
    \item\bibentry{cfbor10b}.
    \item\bibentry{cfbor09a}.
    \item\bibentry{cfbor09b}.
    \item\bibentry{cfbor08a}.
    \item\bibentry{cfbor07a}.
    \item\bibentry{cfbor07b}.
    \item\bibentry{cfbor06a}.
    \item\bibentry{cfbor96a}.
\end{enumerate}

\section*{Non-Refereed Technical Reports}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{rpbor20a}.
    \item\bibentry{rpbor19a}.
    \item\bibentry{rpbor18a}.
    \item\bibentry{rpbor15a}.
    \item\bibentry{rpbor12a}.
    \item\bibentry{rpbor12b}.
    \item\bibentry{rpbor11a}.
    \item\bibentry{rpbor10a}.
    \item\bibentry{rpbor10b}.
    \item\bibentry{rpbor09a}.
    \item\bibentry{rpbor07a}.
    \item\bibentry{rpbor07b}.
    \item\bibentry{rpbor07c}.
    \item\bibentry{rpbor06a}.
\end{enumerate}

\section*{Conference Presentations}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cfpbor19a}.
    \item\bibentry{cfpbor19b}.
    \item\bibentry{cfpbor19c}.
    \item\bibentry{cfpbor19d}.
    \item\bibentry{cfpbor19e}.
    \item\bibentry{cfpbor19f}.
    \item\bibentry{cfpbor18a}.
    \item\bibentry{cfpbor18b}.
    \item\bibentry{cfpbor18c}.
    \item\bibentry{cfpbor18d}.
    \item\bibentry{cfpbor18e}.
    \item\bibentry{cfpbor17a}.
    \item\bibentry{cfpbor17b}.
    \item\bibentry{cfpbor17c}.
    \item\bibentry{cfpbor17d}.
    \item\bibentry{cfpbor17e}.
    \item\bibentry{cfpbor16a}.
    \item\bibentry{cfpbor13a}.
    \item\bibentry{cfpbor13b}.
    \item\bibentry{cfpbor12a}.
    \item\bibentry{cfpbor11a}.
    \item\bibentry{cfpbor10a}.
    \item\bibentry{cfpbor10b}.
    \item\bibentry{cfpbor09a}.
    \item\bibentry{cfpbor09b}.
    \item\bibentry{cfpbor08a}.
    \item\bibentry{cfpbor07a}.
    \item\bibentry{cfpbor07b}.
    \item\bibentry{cfpbor06a}.
\end{enumerate}

\section*{Teaching Experience}
\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE502: Historical examinations of heterogeneity in nuclear criticality safety \hfill{Spring 2020}}\\
\hspace*{\fill}\textit{directed study}\\
Using published nuclear criticality safety references, this course will conduct an examination of the effect of heterogeneity with respect to nuclear criticality safety. As part of the history of nuclear criticality safety, a number of critical experiments have been conducted using arrays of fissile material in an attempt to quantify the effect of heterogeneity in the determination of safe handling limits. In these attempts, a number of low-enriched experiments were examined and converted in their critical dimensions to establish a useful baseline from which other limits could be extrapolated. It is of interest to the field of nuclear criticality safety to improve the understanding of the effect of heterogeneity on the critical characteristics of multiplying fissile systems, particularly in the range of intermediate enrichment. It is of further interest to the field that a methodology be established which can be used to evaluate these types of systems for practical nuclear criticality safety applications, especially the development of nuclear criticality safety limits. To that end, this course will identify relevant data in the literature used to generate historical experiments and apply MCNP to model these experiments in order to understand and evaluate assumptions and restrictions raised in the experiments.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE502: Heterogeneity comparisons of intermediate enrichment uranium in critical systems \hfill{Spring 2020}}\\
\hspace*{\fill}\textit{directed study}\\
Using the International Criticality Safety Benchmark Evaluation Project (ICSBEP) handbook of evaluated critical experiments, conduct an examination of the effect of heterogeneity in intermediate-enrichment uranium systems. The ICSBEP handbook contains descriptions and evaluations of critical experiments conducted in facilities throughout the world. The reach of the handbook stretches to the beginning of the history of nuclear engineering. In those evaluations, a variety of methods have been discussed and described which convert a system of known or unknown degree of heterogeneity into a simplified homogeneous model, which is a traditional method for examining the critical characteristics of multiplying systems. The specific methodology for this conversion varies between evaluations and is explained in some cases, where other cases are less descriptive. It is of interest to the field of nuclear criticality safety to improve the understanding of the effect of heterogeneity on the critical characteristics of multiplying fissile systems, particularly in the range of intermediate enrichment. It is of further interest to the field that a methodology be established which can be used to evaluate these types of systems for practical nuclear criticality safety applications, especially the development of nuclear criticality safety limits. This course will identify and evaluate relevant benchmark experiments for heterogeneity effects using MCNP to establish new baseline models from the benchmark handbook.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE502: Nuclear integrated energy systems \hfill{Spring 2020}}\\
\hspace*{\fill}\textit{directed study}\\
Nuclear renewable hybrid energy systems enable a nuclear reactor to load follow with a renewable energy source. These must be designed to distribute energy dynamically by supplying electricity to the grid while using either thermal or electrical energy for industrial applications. This takes advantage of the flexible distribution of electricity or heat to maximize profit. The industrial process serves as a load sink for the excess heat or electricity produced by the nuclear reactor. Economic challenges to the current United States nuclear light water reactor (LWR) fleet have led to early plant closures. While LWRs primarily deliver baseload electricity, there is no reason why nuclear energy produced by these reactors cannot be used to provide energy to a range of industrial applications. This directed study course will identify feasible systems, products, and commodities that could be produced by existing nuclear plants. As part of this, cost and potential profitability will be analyzed within the context of market structures and grid reliability.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE527: Nuclear material storage, transport, disposal \hfill{Spring 2020}}\\
There is a wide range of nuclear materials that are stored, transported and disposed of each day. The materials include medical radioisotopes, new fuel pellets, used fuel, and industrial radioisotopes. This course will cover the regulations that govern nuclear material storage, transportation and disposal, as well as the engineering requirements and practical aspects of handling these materials.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE535: Nuclear Criticality Safety I \hfill{Spring 2020}}\\
This course applies uses the foundation of applied nuclear physics to develop and explain the international and domestic rules and practices that are used to prevent inadvertent criticality in fuel cycle applications such as used fuel storage and processing.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE585: Nuclear Fuel Cycle Analysis \hfill{Fall 2017}}\\
This course presents the nuclear fuel cycle can as an holistic system with components related in many complex ways. This course focuses on systems analysis of components that comprise the nuclear fuel cycle to understand the contemporary challenges facing nuclear energy.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{TM529: Risk Assessment \hfill{Spring 2019; 2018; 2017; 2016}}\\
This course is designed to provide students with an understanding of how to perform a comprehensive risk assessment applicable to a wide variety of engineering problems in many different disciplines. The course will focus on failure mode and effect analysis, fault tree analysis, probabilistic risk analysis, and human reliability analysis. The course will also cover fundamental probability and statistics content.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE450: Principles of Nuclear Engineering \hfill{Fall 2019; 2018; 2017; 2016; 2015}}\\
In this course, an overview of fundamental nuclear engineering principles and how these are practically applied to contemporary, nuclear engineering problems will be presented.  The topics covered in this course include: nuclear physics and reactions, materials science, radiation protection, energy production, fuel cycle analysis, advanced reactor design, fusion, nonproliferation, back-end management, and risk assessment and safety.  Throughout the course, the ethical considerations with regards to engineering problems within these fields will also be discussed.
\vspace*{.75\baselineskip}

\noindent\textbf{Diablo Valley College $\sq$ Department of Architecture and Engineering}\\
\textbf{Adjunct Professor}\\ 
\textit{ENGIN110: Introduction to Engineering \hfill{Spring 2015; 2014; 2013; Fall 2014}}\\
This course introduces students to fundamental engineering principles. Students learn how these are applied to contemporary engineering problems through laboratory exercises, homework assignments, design projects, interviews with professional engineers, and field trips to engineering companies. Topics include: materials science, risk assessment and safety, critical problem-solving, engineering analysis, engineering design processes, project development, engineering software, and presentation tools. The role of the engineer in society, professionalism, and engineering ethics are major themes. The emphasis is on creative problem-solving, teamwork, and effective communication, both in presentation and writing.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Instructor}\\
\textit{NE92: Issues in Nuclear Science and Engineering \hfill{Fall 2011}}\\
This course provides undergraduate students with an overview of the nuclear engineering profession, including fundamental nuclear engineering principles and how these are practically applied to nuclear engineering problems. The topics covered include nuclear physics and reactions, materials science, radiation protection, energy production, fuel cycle analysis, advanced reactor design, fusion, nonproliferation, back-end management, risk assessment, and safety. Throughout the course, the ethical considerations concerning engineering problems within these fields are also addressed through a comprehensive, student-driven course project.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Instructor}\\
\textit{NE375: Teaching Techniques in Nuclear Engineering \hfill{Fall 2011; 2010}}\\
This course acquaints graduate student instructors (GSIs) with teaching techniques for courses in the Department of Nuclear Engineering. The GSI will have several duties far beyond grading assignments and/or examinations: conducting discussion sessions, review lectures, or laboratory experiments. The GSI, therefore, needs to develop the appropriate tools to use when facing these pedagogical challenges. Three students from the 2010 course received the Outstanding Graduate Student Instructor Award given by the UC-Berkeley Graduate Student Instructor Teaching \& Resource Center.
\vspace*{.75\baselineskip}

\noindent\textbf{The University of Tokyo $\sq$ Department of Nuclear Engineering/Management}\\
\textbf{Part time lecturer}\\
\textit{Technical English for Scientists \hfill{Winter, Summer 2008; Winter 2007}}\\
This course provided the opportunity for non-native English speaking students to develop technical communication skills; i.e., presenting scientific and technical material to an informed audience at an international conference. In this course, the ‘assertion evidence design’ concept for technical presentation of scientific topics was applied to student research interests. Transmutable skills focused on the professional communication of scientific research in various public speaking formats and a comfortable familiarity with the English language to establish a stronger foundation for technical writing.

>>>>

%.bst file
\bibliographystyle{} %custom bst file

@@

\noindent\textbf{University}\\
\textbf{Master of Science $\sq$ Major} \hfill{\textit{Date}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Thesis: }
    \item[]Advisor: 
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University}\\
\textbf{Bachelor of Science $\sq$ Major and distinction(s)} \hfill{\textit{}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Capstone: }
    \item[] Advisor: 
\end{itemize}

\section*{Research Experience} %academic positions
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary 
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary

\section*{Related Research Experience} %like internships
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary 
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary

\section*{Related Professional Experience} %anything else
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary 
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary

\section*{Awarded Projects} %chronologically
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{enumerate}

\section*{Thesis Committees}
\subsection*{Major Professor} %or adviser, whatever the official title is
\noindent\textit{Current}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Student Name, Degree - Topic
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Student Name, Degree - Thesis Title 
\end{itemize}

\subsection*{Member}
\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Student Name, Degree - Thesis Title 
\end{itemize}

\section*{Refereed Journal Publications}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{pr1}.
\end{enumerate}

\section*{Book Contribution}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{bk1}.
\end{enumerate}

\section*{Refereed Conference Proceedings}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cf1}.
\end{enumerate}

\section*{Non-Refereed Technical Reports}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{rp1}.
\end{enumerate}

\section*{Conference Presentations}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cf1}.
\end{enumerate}

\section*{Teaching Experience}
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary

\section*{Related Teaching Experience} %for TA, etc.
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary

\section*{Professional Service} 
\subsection*{University/Institution} %department/college related activities
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Academic Search Committees}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Year}
    \item[]Search committee %don't say it was a failed search 
            \vspace{.05in}
    \item[]\textit{Year}
    \item[]Search committee %don't say it was a failed search 
\end{itemize}

\subsection*{Peer Reviewer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Regular periods} %for journals/conferences on a regular basis
    \item[] 
            \vspace{.05in}
    \item[]\textit{Year} %specific one-time reviewing
    \item[] 
            \vspace{.05in}
    \item[]\textit{Year} %specific one-time reviewing
    \item[] 
\end{itemize}

\subsection*{Conference Committees}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Technical Session Organizer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Technical Session Chair}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Symposia Organizer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Invited Talks}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{University/Institution $\sq$ Department} %speaking at graduate orientation, etc.
    \item[]Title $\sq$ Purpose \hfill{\textit{Dates}}
        \vspace{.05in}
    \item[]\textit{Seminars} %typical department seminar talks
    \item[]University/Institution Department \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textit{Lightning Talks} %throw everything in there 
    \item[]Talk \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textit{Outreach}
    \item[]Event \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textit{Lectures} %invited to lecture in a course
    \item[]University/Institution - Course or topic \hfill{\textit{Date}}
\end{itemize}

\subsection*{Community Service}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Event} \hfill{\textit{Date}}
    \item[]Summary 
        \vspace{.05in}
    \item[]\textit{Event} \hfill{\textit{Date}}
    \item[]Summary 
\end{itemize}

\subsection*{Outreach and Related Professional Activities} %career fairs, etc.
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Event \hfill{\textit{Date}}
\end{itemize}

\subsection*{Professional Training}
\noindent\textbf{University/Institution}\\
\textbf{Role}\\
\textit{Title of Event} \hfill{\textit{Date}}\\
Summary
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution}\\
\textbf{Role}\\
\textit{Title of Event} \hfill{\textit{Date}}\\
Summary

\subsection*{Awards and Fellowships}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textbf{University/Institution}
    \item[]Award or fellowship \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textbf{University/Institution}
    \item[]Award or fellowship \hfill{\textit{Date}}

\subsection*{Professional Societies and Positions}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textbf{Society}
    \item[]Position \hfill{\textit{From - To}}
        \vspace{.05in}
    \item[]\textbf{Society}
    \item[]Position \hfill{\textit{From - To}}
\end{itemize}
